Component response rate variation drives stability in large complex systems

### 2018-07-28 notebook/ms.Rmd
First Discussion sentence

This suggests that the stability of large systems might be dependent upon variation in the response rate of their individual components, meaning that factors such as generation time (in ecological networks), transaction speed (in economic networks), or communication speed (in social networks) needs to be considered when investigating the stability of complex systems. *Cite @Ahmadian2015 here*?

>>>>

Here I have shown that the stability of large systems might be contigent upon variation in the response rates of their individual components, meaning that factors such as generation time and rate of trait evolution (in biological networks), transaction speed (in economic networks), or communication speed (in social networks) need to be considered when investigating the stability of complex systems. *Cite @Ahmadian2015 here*?
